Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-12 manuscript/manuscript.tex
Fix typo

For an exponential density function, the density-based discretization will be applied
before the adaptive discretization algorithm.
This means that optimal values for both the distance-size ratio $D$ and the delta ratio
$\delta$ must be determined.
We perform an error analysis similar to what was done for the linear density case.
But, now the spherical shell will have an exponential density function that assumes the
values of $\rho_\text{out} = 2670$~kg/m$^3$ and $\rho_\text{in} = 3300$~kg/m$^3$ on the
outer and inner surfaces, respectively, defined as follows:
by

>>>>

For an exponential density function, the density-based discretization will be applied
before the adaptive discretization algorithm.
This means that optimal values for both the distance-size ratio $D$ and the delta ratio
$\delta$ must be determined.
We perform an error analysis similar to what was done for the linear density case.
But, now the spherical shell will have an exponential density function that assumes the
values of $\rho_\text{out} = 2670$~kg/m$^3$ and $\rho_\text{in} = 3300$~kg/m$^3$ on the
outer and inner surfaces, respectively, defined as follows:
